Untitled

### 2024-11-01 code/manuscript_altanalysis.Rmd
finalized stratified analysis

df.temptemp %>% 
  mutate(Post = ifelse(year.rel >= 0, 1, 0)) %>% 
  group_by(Post, Treat) %>% 
  select(Qcomp:Closed) %>% 
  summarise_all(mean.nas) %>% 
  # summarise(Total = mean(Total, na.rm = TRUE), 
  #           Quality = mean(Qcomp, na.rm = TRUE), 
  #           Finances = mean(Altman, na.rm = TRUE)) %>% 
  pivot_longer(cols = Qcomp:Closed) %>% 
  mutate(value = round(value, 2)) %>% 
  #filter(name %in% c("Total", "Qcomp", "Altman")) %>% 
  pivot_wider(id_cols = name, names_from = c(Treat, Post), values_from = value) %>% 
  mutate(Unadjusted = (Treated_1 - Treated_0) - (Control_1 - Control_0)) %>% 
  cbind(core.did.estimates) %>% 
   select(name, `Control_0`, `Control_1`, `Treated_0`, `Treated_1`, Unadjusted, Estimate, `95% CI`, Pr...t..) %>% 
  mutate(`% Change` = round(Estimate / `Treated_0` * 100, 1)) %>% 
  rename(Outcome = name) %>% 
  select(Outcome:Estimate, `95% CI`, Pr...t.., `% Change`) %>% 
  kable("html", booktabs = T, col.names = c("Outcome","Pre","Post","Pre","Post","Unadjusted DID","Estimate","95% CI","p-value", "% Change")) %>% 
  kable_styling(latex_options = c("striped")) %>%
  #pack_rows(index = c("Total Patients by Insurnace" = 4, "Quality Measure Components" = 6, "Financial Components" = 4)) %>% 
  add_header_above(c(" " = 1, "Control" = 2, "Treated" = 2, " " = 1, "Staggered DID" = 4))

df.temptemp %>% mutate(Tx = ifelse(Year >= Att & Att %notin% c(0, 2009, 2010), 1, 0)) %>% filter(!is.na(Tx)) %>% 
  ungroup() %>% 
  filter(!is.na(value)) %>% 
  select(Year, Closed) %>% 
  group_by(Year) %>% 
  summarize(mean(Closed))

@@

coeffs.did.strat <- c(0,0,0,0, 0, 0, 0, 0, 0, 0, 0, 0)

@@

  #df.temptemptemp <- df.temptemp %>% mutate(Tx = ifelse(Tx > 1, 1, 0)) %>% filter(!is.na(Tx)) #%>% group_by(ID) %>% mutate(EarlyHHI = first(ClinicHHI, na_rm = TRUE)) %>% filter(EarlyHHI < 9000)
  df.temptemptemp <- df.temptemp %>% mutate(Tx = ifelse(Year >= Att & Att %notin% c(0, 2009, 2010), 1, 0)) %>% filter(!is.na(Tx)) #%>% filter(Att %notin% c(2011))
  colnames(df.temptemptemp)[(16+k)] <- "Outcome"
  # Winsorized
  outlier.vals <- quantile(df.temptemptemp$Outcome, p = c(0.01, 0.99), na.rm = TRUE)
  df.temptemptemp <- df.temptemptemp %>% 
    mutate(Outcome = ifelse(Outcome <= outlier.vals[1], outlier.vals[1], 
                            ifelse(Outcome >= outlier.vals[2], outlier.vals[2], Outcome)))
  model <-  did2s(
      data = df.temptemptemp, 
      yname = "Outcome", 
      treatment = "Tx",
        first_stage = ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + UrbanRuralFlag | ID + Year , #Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.MCD + Pct.MCR + Pct.None | ID + Year , 
        second_stage =~ i(Tx*ifelse(value_min== 1, 1, 0), ref = FALSE) + i(Tx*ifelse(value_min==2, 1, 0), ref = FALSE) + i(Tx*ifelse(value_min>= 3, 1, 0), ref = FALSE),
        cluster_var = "ID",
      verbose = TRUE
    )

  coeffs.did.strat <- rbind(coeffs.did.strat, c(model$coeftable[1,], model$coeftable[2,], model$coeftable[3,]))

@@

core.did.estimates.strat <- data.frame(cbind(colnames(df.temptemp)[17:39], (coeffs.did.strat[-1,]))) %>% 
  #select(V1, Estimate, Pr...t.., Estimate.1, Pr...t...1) %>% 
  mutate(EstimateFirst = round(as.numeric(Estimate), 2), `95% CI First` = paste(round(as.numeric(Estimate) - 1.96 * as.numeric(Std..Error), 2), ", ", round(as.numeric(Estimate) + 1.96 * as.numeric(Std..Error), 2), sep = "")) %>% 
  mutate(EstimateSecond = round(as.numeric(Estimate.1), 2), `95% CI Second` = paste(round(as.numeric(Estimate.1) - 1.96 * as.numeric(Std..Error.1), 2), ", ", round(as.numeric(Estimate.1) + 1.96 * as.numeric(Std..Error.1), 2), sep = "")) %>% 
  mutate(EstimateMore = round(as.numeric(Estimate.2), 2), `95% CI More` = paste(round(as.numeric(Estimate.2) - 1.96 * as.numeric(Std..Error.2), 2), ", ", round(as.numeric(Estimate.2) + 1.96 * as.numeric(Std..Error.2), 2), sep = "")) %>% 
  select(V1, EstimateFirst, `95% CI First`, Pr...t.., EstimateSecond, `95% CI Second`, Pr...t...1, EstimateMore, `95% CI More`, Pr...t...2)

@@

core.did.estimates.strat

did2s(
      data = df.temptemptemp, 
      yname = "Outcome", 
      treatment = "Tx",
        first_stage = ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + UrbanRuralFlag | ID + Year , #Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.MCD + Pct.MCR + Pct.None | ID + Year , 
        second_stage =~ i(Tx*as.numeric(value_first)) ,
        cluster_var = "ID",
      verbose = TRUE
    )

>>>>

df.temptemp %>% 
  mutate(Post = ifelse(year.rel >= 0, 1, 0)) %>% 
  group_by(Post, Treat) %>% 
  select(Qcomp:Staff) %>% 
  summarise_all(mean.nas) %>% 
  # summarise(Total = mean(Total, na.rm = TRUE), 
  #           Quality = mean(Qcomp, na.rm = TRUE), 
  #           Finances = mean(Altman, na.rm = TRUE)) %>% 
  pivot_longer(cols = Qcomp:Staff) %>% 
  mutate(value = round(value, 2)) %>% 
  #filter(name %in% c("Total", "Qcomp", "Altman")) %>% 
  pivot_wider(id_cols = name, names_from = c(Treat, Post), values_from = value) %>% 
  mutate(Unadjusted = (Treated_1 - Treated_0) - (Control_1 - Control_0)) %>% 
  rbind(

    cbind(name = "Closed", 
    df.temptemp %>% 
  mutate(Post = ifelse(year.rel >= 0, 1, 0)) %>% 
  filter(!is.na(value)) %>% 
  group_by(Post, Treat) %>% 
  select(Closed) %>% 
  summarise_all(mean.nas) %>% 
  # summarise(Total = mean(Total, na.rm = TRUE), 
  #           Quality = mean(Qcomp, na.rm = TRUE), 
  #           Finances = mean(Altman, na.rm = TRUE)) %>% 
  #mutate(value = round(value, 2)) %>% 
  #filter(name %in% c("Total", "Qcomp", "Altman")) %>% 
  pivot_wider(names_from = c(Treat, Post), values_from = Closed) %>% 
  mutate(Unadjusted = (Treated_1 - Treated_0) - (Control_1 - Control_0)))

  ) %>%

  cbind(core.did.estimates) %>% 
   select(name, `Control_0`, `Control_1`, `Treated_0`, `Treated_1`, Unadjusted, Estimate, `95% CI`, Pr...t..) %>% 
  mutate(`% Change` = round(Estimate / `Treated_0` * 100, 1)) %>% 
  rename(Outcome = name) %>% 
  select(Outcome:Estimate, `95% CI`, Pr...t.., `% Change`) %>% 
  kable("html", booktabs = T, col.names = c("Outcome","Pre","Post","Pre","Post","Unadjusted DID","Estimate","95% CI","p-value", "% Change")) %>% 
  kable_styling(latex_options = c("striped")) %>%
  #pack_rows(index = c("Total Patients by Insurnace" = 4, "Quality Measure Components" = 6, "Financial Components" = 4)) %>% 
  add_header_above(c(" " = 1, "Control" = 2, "Treated" = 2, " " = 1, "Staggered DID" = 4))

@@

coeffs.did.strat <- c(0,0,0,0, 0, 0, 0, 0)

@@

  #df.temptemptemp <- df.temptemp %>% mutate(Tx = ifelse(Tx > 1, 1, 0)) %>% filter(!is.na(Tx)) #%>% group_by(ID) %>% mutate(EarlyHHI = first(ClinicHHI, na_rm = TRUE)) %>% filter(EarlyHHI < 9000)
  df.temptemptemp <- df.temptemp %>% mutate(Tx = ifelse(Year >= Att & Att %notin% c(0, 2009, 2010), 1, 0)) %>% filter(!is.na(Tx)) #%>% filter(Att %notin% c(2011))
  colnames(df.temptemptemp)[(16+k)] <- "Outcome"
  # Winsorized
  outlier.vals <- quantile(df.temptemptemp$Outcome, p = c(0.01, 0.99), na.rm = TRUE)
  df.temptemptemp <- df.temptemptemp %>% 
    mutate(Outcome = ifelse(Outcome <= outlier.vals[1], outlier.vals[1], 
                            ifelse(Outcome >= outlier.vals[2], outlier.vals[2], Outcome)))

   model <-  did2s(
      data = df.temptemptemp,
      yname = "Outcome",
      treatment = "Tx",
        first_stage = ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + UrbanRuralFlag | ID + Year , #Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.MCD + Pct.MCR + Pct.None | ID + Year ,
        second_stage =~ i(Tx*ifelse(value_min== 1, 1, 0), ref = FALSE) + i(Tx*ifelse(value_min>=2, 1, 0), ref = FALSE),
        #second_stage =~ i(Tx, ref = FALSE) + I(as.numeric(Tx) * as.numeric(value_min)) ,
        cluster_var = "ID",
      verbose = TRUE
    )

  coeffs.did.strat <- rbind(coeffs.did.strat, c(model$coeftable[1,], model$coeftable[2,]))

@@

core.did.estimates.strat <- data.frame(cbind(colnames(df.temptemp)[17:39], (coeffs.did.strat[-1,]))) %>%
  #select(V1, Estimate, Pr...t.., Estimate.1, Pr...t...1) %>%
  mutate(EstimateFirst = round(as.numeric(Estimate), 2), `95% CI First` = paste(round(as.numeric(Estimate) - 1.96 * as.numeric(Std..Error), 2), ", ", round(as.numeric(Estimate) + 1.96 * as.numeric(Std..Error), 2), sep = "")) %>%
  mutate(EstimateSecond = round(as.numeric(Estimate.1), 2), `95% CI Second` = paste(round(as.numeric(Estimate.1) - 1.96 * as.numeric(Std..Error.1), 2), ", ", round(as.numeric(Estimate.1) + 1.96 * as.numeric(Std..Error.1), 2), sep = "")) %>%
  select(V1, EstimateFirst, `95% CI First`, Pr...t.., EstimateSecond, `95% CI Second`, Pr...t...1)

@@

core.did.estimates.strat[c(1, 2, 3, 4, 11:13, 16:23),]

#   model <-  did2s(
#       data = df.temptemptemp,
#       yname = "Outcome",
#       treatment = "Tx",
#         first_stage = ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + UrbanRuralFlag | ID + Year , #Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.MCD + Pct.MCR + Pct.None | ID + Year ,
#         second_stage =~ i(Tx*ifelse(value_min== 1, 1, 0), ref = FALSE) + i(Tx*ifelse(value_min==2, 1, 0), ref = FALSE) + i(Tx*ifelse(value_min>= 3, 1, 0), ref = FALSE),
#         cluster_var = "ID",
#       verbose = TRUE
#     )
# 
#   coeffs.did.strat <- rbind(coeffs.did.strat, c(model$coeftable[1,], model$coeftable[2,], model$coeftable[3,]))
# 
# 
# }
# 
# 
# core.did.estimates.strat <- data.frame(cbind(colnames(df.temptemp)[17:39], (coeffs.did.strat[-1,]))) %>%
#   #select(V1, Estimate, Pr...t.., Estimate.1, Pr...t...1) %>%
#   mutate(EstimateFirst = round(as.numeric(Estimate), 2), `95% CI First` = paste(round(as.numeric(Estimate) - 1.96 * as.numeric(Std..Error), 2), ", ", round(as.numeric(Estimate) + 1.96 * as.numeric(Std..Error), 2), sep = "")) %>%
#   mutate(EstimateSecond = round(as.numeric(Estimate.1), 2), `95% CI Second` = paste(round(as.numeric(Estimate.1) - 1.96 * as.numeric(Std..Error.1), 2), ", ", round(as.numeric(Estimate.1) + 1.96 * as.numeric(Std..Error.1), 2), sep = "")) %>%
#   mutate(EstimateMore = round(as.numeric(Estimate.2), 2), `95% CI More` = paste(round(as.numeric(Estimate.2) - 1.96 * as.numeric(Std..Error.2), 2), ", ", round(as.numeric(Estimate.2) + 1.96 * as.numeric(Std..Error.2), 2), sep = "")) %>%
#   select(V1, EstimateFirst, `95% CI First`, Pr...t.., EstimateSecond, `95% CI Second`, Pr...t...1, EstimateMore, `95% CI More`, Pr...t...2)
# 
# core.did.estimates.strat <- core.did.estimates.strat
# rownames(core.did.estimates.strat) <- NULL
# 
# core.did.estimates.strat[c(1, 2, 3, 4, 11:13, 16:23),]

did2s(
      data = df.temptemptemp, 
      yname = "Qcomp", 
      treatment = "Tx",
        first_stage = ~ Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless + UrbanRuralFlag | ID + Year , #Pct.NHA + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.MCD + Pct.MCR + Pct.None | ID + Year , 
        second_stage =~ i(Tx, ref = FALSE) + I(as.numeric(Tx) * as.numeric(value_first - 1)) ,
        cluster_var = "ID",
      verbose = TRUE
    )
